% CV for Furkan Doğmuş — Oxford/AltaCV Style
% Overleaf'te "Oxford" temalı moderncv ile derlenir
% 1. Overleaf'te New Project → Upload Project
% 2. Bu .tex dosyasını yükle
% 3. Menu'den Compiler: XeLaTeX veya pdfLaTeX seç
% 4. Recompile

\documentclass[11pt,a4paper,sans]{moderncv}

% Oxford stili
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.8]{geometry}

% ─── Kişisel Bilgiler ─────────────────────────────────────────
\name{Furkan}{Doğmuş}
\title{DevOps Engineer}
\phone[mobile]{+90 551 068 33 16}
\email{furkandogmus9183@gmail.com}
\social[linkedin]{furkandogmus}
\social[github]{furkandogmus}
\extrainfo{Ankara, Turkey}

\quote{Cloud and DevOps-focused engineer with 2 years of experience in CI/CD automation, monitoring, Kubernetes, and backup/disaster recovery. Passionate about cloud-native infrastructure, GitOps, observability, and platform engineering.}

\begin{document}

\makecvtitle

% ─── Deneyim ──────────────────────────────────────────────────
\section{Experience}

\cventry{May 2024 -- May 2026}
{DevOps / Backend Engineer}
{BTS Group -- ODTÜ Teknokent}
{Ankara, Turkey}
{}{
\begin{itemize}
    \item Integrated enterprise backup and disaster recovery solutions using NetBackup and Commvault.
    \item Implemented full VM recovery, cross-host restoration, disk recovery, and provisioning from backup images.
    \item Reduced deployment time from 30 to 10 minutes by automating RPM builds via GitLab CI pipelines.
    \item Built 3+ Grafana dashboards for CPU, memory, disk I/O, network, and container metrics.
    \item Collected infrastructure metrics with Prometheus, libvirt exporter, and node/container exporters.
    \item Designed centralized logging with ELK Stack and Filebeat for application log aggregation.
\end{itemize}
}

% ─── Projeler ─────────────────────────────────────────────────
\section{Projects}

\cventry{2025 -- Present}
{BotForge --- Multi-tenant RAG Chatbot Platform}
{\href{https://botforge.bagajpark.com}{botforge.bagajpark.com}}
{}{}
{
\begin{itemize}
    \item Multi-tenant AI chatbot platform with document-based RAG, authentication, subscription, and analytics.
    \item Vector search via PostgreSQL + pgvector, containerized CI/CD with Docker and K3d.
    \item \textbf{Stack:} Java, Spring Boot, PostgreSQL, pgvector, Docker, K3d
\end{itemize}
}

\cventry{2025}
{BagajPark --- Luggage Storage Marketplace}
{\href{https://bagajpark.com}{bagajpark.com}}
{}{}
{
\begin{itemize}
    \item Full-stack marketplace with role-based auth, QR tracking, and payment integration.
    \item Automated CI/CD deployment pipelines.
    \item \textbf{Stack:} Next.js, PostgreSQL, Redis, Docker
\end{itemize}
}

\cventry{2026 -- Present}
{RAG Operator for Kubernetes (Ongoing)}
{}{}{}
{
\begin{itemize}
    \item Kubernetes-native operator for declarative RAG ingestion, embedding, and vector indexing.
    \item Uses controller-runtime pattern with CRDs.
    \item \textbf{Stack:} Go, Kubernetes, controller-runtime
\end{itemize}
}

% ─── Eğitim ───────────────────────────────────────────────────
\section{Education}

\cventry{Sep 2021 -- Jan 2026}
{B.Sc. in Computer Engineering}
{Hacettepe University}
{Ankara, Turkey}
{}
{}

% ─── Yetenekler ───────────────────────────────────────────────
\section{Technical Skills}

\cvitem{Cloud \& DevOps}{
Docker, Kubernetes, GitLab CI/CD, Helm, Rocky Linux, Prometheus, Grafana, ELK Stack, Filebeat, NetBackup, Commvault
}
\cvitem{Programming}{
Go, Java, Python, JavaScript, TypeScript, Bash
}
\cvitem{Infrastructure}{
PostgreSQL, Redis, NFS, Ceph, libvirt/KVM, pgvector
}
\cvitem{Platforms}{
Linux (Rocky, Ubuntu), Git, GitHub, GitLab, Jira
}

% ─── Diller ───────────────────────────────────────────────────
\section{Languages}

\cvitemwithcomment{Turkish}{Native}{}
\cvitemwithcomment{English}{Professional Working Proficiency (B2)}{}

% ─── Sertifikalar ─────────────────────────────────────────────
\section{Certifications (In Progress)}

\cventry{Planned}{CKA --- Certified Kubernetes Administrator}{}{}{}{}
\cventry{Planned}{CKAD --- Certified Kubernetes Application Developer}{}{}{}{}
\cventry{Planned}{CKS --- Certified Kubernetes Security Specialist}{}{}{}{}

\end{document}
